Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2017-03-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added new summary tables to Ch 8

>>>>

\begin{table}[h]
  \small
  \centering
  \begin{tabular}{|c|c|c|c|} \hline 
Char Criteria 					&  \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	  	  \\
\hline								&  RI=5					&  RI=10			&  RI=20            \\
\hline Tign=360~$^\circ~C$  	&  0.72					&  1.04				&	0.86			    \\
\hline Tign=515~$^\circ~C$		&  0.48					&  0.72				&   0.62                \\
\hline Tign=565~$^\circ~C$		&  na					&  na				&   na                  \\ 
\hline  CHF=15.0~kW/m$^2$		&  1.36     			& 1.44 		        &   1.40                \\
\hline  CHF=17.5~kW/m$^2$		&  1.12					& 1.40				&   1.40                \\
\hline  CHF=20.0~kW/m$^2$		&  1.04					& 1.36				&   1.36                \\
\hline	CHF=25.~kW/m$^2$		&  0.88					& 1.28				&   1.26 	            \\
\hline  CHF=30.0~kW/m$^2$   	&  0.80					& 1.12				&   1.16			    \\  \hline
  \end{tabular}
  \caption[Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner compartment wall experiments.]{Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner against the compartment wall experiments.  Values from three plume resolution indexes (RI) are shown.  The measured value for the peak fire pattern height was  0.74~$\pm$~0.12. na indicates that the value was not reached on the wall in the simulation.}
  \label{tab:FDS_IGNT_CHF_Wall}
\end{table}

\begin{table}[h]
  \small
  \centering
  \begin{tabular}{|c|c|c|c|} \hline 
Char Criteria 					& \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	\\
\hline								&  RI=5					&  RI=10			&  RI=20            \\
\hline Tign=360~$^\circ~C$  	&  1.60					&  1.56				&  1.56				    \\
\hline Tign=515~$^\circ~C$		&  1.04					&  0.96				&  0.96                 \\
\hline Tign=565~$^\circ~C$		&  0.72					&  na				&  na                   \\
\hline  CHF=15.0~kW/m$^2$		&  2.08    				&  1.84		        &  1.94                 \\
\hline  CHF=17.5~kW/m$^2$		&  2.00					&  1.80				&  1.90                 \\
\hline  CHF=20.0~kW/m$^2$		&  1.92					&  1.76				&  1.86	                \\
\hline	CHF=25.~kW/m$^2$		&  1.76     			&  1.68				&  1.80	                \\
\hline  CHF=30.0~kW/m$^2$   	&  1.44 				&  1.60				&  1.60   				\\  \hline
  \end{tabular}
  \caption[Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner compartment corner experiments.]{Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner against the compartment corner experiments.  Values from three plume resolution indexes (RI) are shown.  The measured value for the peak fire pattern height was  0.74~$\pm$~0.13.  na indicates that the value was not reached on the wall in the simulation.}    
  \label{tab:FDS_IGNT_CHF_Corner}
\end{table}
